\Huge \scshape \fontfamily{pbk}\fontsize{50}{40}\selectfont The Dark \LaTeX{} \\ \medskip \normalfont \medskip\Huge An Example of the dndbook Class

### 2024-10-27 article.tex
Added spanning title in multi-column table example
Removed listparagraph with the simpler "description" environment as per sargeant (see commits https://github.com/sargeant/DND-5e-LaTeX-Template/commit/700737d4a58f9732a41e97a069d3f2d6aa70b96a and https://github.com/sargeant/DND-5e-LaTeX-Template/commit/c9fd42d9395711ee4934f0ecc820b6dd64c30693)

\subsubsection{Hanging Indent Features}
The |listparagraph| format allows hanging indented
lists of options, such as those used for class features,
background skill/tool proficiency options, and
sometimes area features, for example:

\listparagraph[6pt]{Doors}
{The doors are made from thick lumber and are unlocked.}

\listparagraph{Light}
{The area is illuminated by candles placed in sconces on the
walls. Each candle has had a \textit{continual flame} spell
cast on it. Dispelling a flame is rumoured to give grievous offence
to the host.}

\listparagraph{Ventilation}
{All areas contain an adequate air supply. The air is renewed
via lung-like sacks that cling to the ceiling.}

@@

\begin{lstlisting}[basicstyle=\ttfamily\small]
\begin{multicols}{2}
\begin{DndAltTable}[header=Encounters]{cX}
...
\end{DndAltTable}
\begin{DndAltTable}[header=~]{cX}
...
\end{DndAltTable}
\end{multicols}
\end{lstlisting}

@@

\begin{multicols}{2}
\begin{DndAltTable}[header=Encounters]{cX}
    \textbf{d10} & \textbf{Encounter} \\
    1  & Toppled statue \\
    2  & Ferocious kitten \\
    3  & Broken sign \\
    4  & Blind beggar \\
    5  & Piercing wail \\
\end{DndAltTable}
\begin{DndAltTable}[header=~]{cX}
    \textbf{d10} & \textbf{Encounter} \\
    6  & Pack of wolves \\
    7  & Drunk owlbear \\
    8  & Freed prisoners \\
    9  & Wild magic zone \\
    10 & Magic item \\
\end{DndAltTable}
\end{multicols}

>>>>

\subsubsection{Hanging Indent Features}
The |{description}| environment allows hanging indented
lists of options, such as those used for class features,
background skill/tool proficiency options, and
sometimes area features, for example:

\begin{description}
  \item[Doors.]
  The doors are made from thick lumber and are unlocked.

  \item[Light.]
  The area is illuminated by candles placed in sconces on the
  walls. Each candle has had a \textit{continual flame} spell
  cast on it. Dispelling a flame is rumoured to give grievous offence
  to the host.

  \item[Ventilation.]
  All areas contain an adequate air supply. The air is renewed
  via lung-like sacks that cling to the ceiling.
\end{description}

@@

\begin{lstlisting}[basicstyle=\ttfamily\small]
\begin{multicols}{2}
\begin{DndAltTable}[header=Encounters~(With~Spanning~Title)]{cX}
...
\end{DndAltTable}
\begin{DndAltTable}[header=~]{cX}
...
\end{DndAltTable}
\end{multicols}
\end{lstlisting}

@@

\begin{multicols}{2}
\begin{DndAltTable}[header=Encounters~(With~Spanning~Title)]{cX}
    \textbf{d10} & \textbf{Encounter} \\
    1  & Toppled statue \\
    2  & Ferocious kitten \\
    3  & Broken sign \\
    4  & Blind beggar \\
    5  & Piercing wail \\
\end{DndAltTable}
\begin{DndAltTable}[header=~]{cX}
    \textbf{d10} & \textbf{Encounter} \\
    6  & Pack of wolves \\
    7  & Drunk owlbear \\
    8  & Freed prisoners \\
    9  & Wild magic zone \\
    10 & Magic item \\
\end{DndAltTable}
\end{multicols}

### 2024-10-27 example.tex
Removed listparagraph with the simpler "description" environment as per sargeant (see commits https://github.com/sargeant/DND-5e-LaTeX-Template/commit/700737d4a58f9732a41e97a069d3f2d6aa70b96a and https://github.com/sargeant/DND-5e-LaTeX-Template/commit/c9fd42d9395711ee4934f0ecc820b6dd64c30693)

\subsubsection{Hanging Indent Features}
The |\listparagraph| format allows hanging indented
lists of options, such as those used for class features,
background skill/tool proficiency options, and
sometimes area features, for example:

\listparagraph[6pt]{Doors}
{The doors are made from thick lumber and are unlocked.}

\listparagraph{Light}
{The area is illuminated by candles placed in sconces on the
walls. Each candle has had a \textit{continual flame} spell
cast on it. Dispelling a flame is rumoured to give grievous offence
to the host.}

\listparagraph{Ventilation}
{All areas contain an adequate air supply. The air is renewed
via lung-like sacks that cling to the ceiling.}

>>>>

\subsubsection{Hanging Indent Features}
The |{description}| environment allows hanging indented
lists of options, such as those used for class features,
background skill/tool proficiency options, and
sometimes area features, for example:

\begin{description}
  \item[Doors.]
  The doors are made from thick lumber and are unlocked.

  \item[Light.]
  The area is illuminated by candles placed in sconces on the
  walls. Each candle has had a \textit{continual flame} spell
  cast on it. Dispelling a flame is rumoured to give grievous offence
  to the host.

  \item[Ventilation.]
  All areas contain an adequate air supply. The air is renewed
  via lung-like sacks that cling to the ceiling.
\end{description}
